DeepSphere: a graph-based spherical CNN

### 2019-11-12 main.tex

\paragraph{Theoretical convergence.}
We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme. \mart{Here we insert the definition of the extended graph laplacian and of the rotation operator Rg} Following their setting, we define the extended graph Laplacian operator as a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
	\begin{equation}
	\label{eq:Heat Kernel Graph Laplacian operator}
	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
	\end{equation}
Note that we have the following relation $\b{L}_n^t \b{f} = T_\V L_n^t f$.
Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, we also define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area and $d_i$ the radius of the smallest ball in $\R^3$ containing $\sigma_i$ and centered at $x_i$. Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$. Given any rotation $g\in SO(3)$, we define the corresponding rotation operator $\mathcal R_g$ such that for any function $f$ on the sphere 
\begin{equation}\label{eq:rotation operator}
\mathcal R_g f(x) := f(g^{-1}(x)).
\end{equation}
\begin{theorem}
	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$, $\beta\in\mathbb R$ such that 
% 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  
	\begin{equation*}
		\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) = \frac{1}{|\S^2|}\triangle_{\S^2}f(y)
	\end{equation*} 
% 	for $n\to\infty$.
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
As a direct implication of this theorem, the rescaled operator $\hat L_n^{t_n} := \frac{|\mathbb S^2|}{4\pi t^2}L_n^{t_n}$ (and its discrete counterpart $ \mathbf{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2} \mathbf L$) converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \cite{belkin2007convergence}. This operator commutes with rotation and hence this convergence is a strong hint for equivariance, as formalized in the following proposition.
%%%%%%%%%%%%%%%%%%%%%%%  link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{prop}\label{prop:equivariance}
Under the hypothesis of theorem \ref{theo:pointwise convergence for a regular sampling}, we have the following pointwise convergence for the rescaled graph Laplacian 
\begin{equation*}
\forall y\in\mathbb S^2\quad\left| \mathcal R_g \hat L_n^{t_n} f (y) - \hat L_n^{t_n} \mathcal R_g f(y) \right| \xrightarrow{n\to\infty}0.
\end{equation*}
\end{prop}
%%%%%%%%%%%%%%%%%%%%%%% end of link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\paragraph{Theoretical convergence.}
We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme. \mart{Here we insert the definition of the extended graph laplacian and of the rotation operator Rg} Following their setting, we define the extended graph Laplacian operator as a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
	\begin{equation}
	\label{eq:Heat Kernel Graph Laplacian operator}
	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
	\end{equation}
Note that we have the following relation $\b{L}_n^t \b{f} = T_\V L_n^t f$.
Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, we define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area, and $d_i$ the radius of the smallest ball in $\R^3$ containing $\sigma_i$ and centered at $x_i$.%\footnote{$d_i$ should be understood as the largest distance between the center $x_i$ and any point on the surface $sigma_i$.}
Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
Given any rotation $g\in SO(3)$, we define the corresponding rotation operator $\mathcal R_g$ such that for any function $f$ on the sphere
\begin{equation}\label{eq:rotation operator}
	\mathcal R_g f(x) := f(g^{-1}(x)).
\end{equation}
\begin{theorem}
	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$, $\beta\in\mathbb R$ such that 
% 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  
	\begin{equation*}
		\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) = \frac{1}{|\S^2|}\triangle_{\S^2}f(y).
	\end{equation*} 
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
As a direct implication of this theorem, the rescaled operator $\hat L_n^{t_n} := \frac{|\mathbb S^2|}{4\pi t^2}L_n^{t_n}$ (and its discrete counterpart $ \mathbf{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2} \mathbf L$) converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \cite{belkin2007convergence}. This operator commutes with rotation and hence this convergence is a strong hint for equivariance, as formalized in the following proposition.
%%%%%%%%%%%%%%%%%%%%%%%  link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{prop}\label{prop:equivariance}
Under the hypothesis of theorem \ref{theo:pointwise convergence for a regular sampling}, we have the following pointwise convergence for the rescaled graph Laplacian 
\begin{equation*}
\forall y\in\mathbb S^2\quad\left| \mathcal R_g \hat L_n^{t_n} f (y) - \hat L_n^{t_n} \mathcal R_g f(y) \right| \xrightarrow{n\to\infty}0.
\end{equation*}
\end{prop}
%%%%%%%%%%%%%%%%%%%%%%% end of link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%
